---
output: github_document
---

# pubmedr

`pubmedr` is an R package designed to fetch and process data from the PubMed database. The package provides functions to build search URLs, retrieve search results, and process paper entries to extract relevant information.

## Installation

To install the package, you can use the `devtools` package to install it from a local directory or GitHub repository.

```{r installation, eval=FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}

# install "pubmedr" from a local directory, where you `git clone` pubmedr
devtools::install("path/to/pubmedr")

# or install directly from GitHub
devtools::install_github("danymukesha/pubmedr")
```

## Usage

Below are detailed steps on how to use the `pubmedr` package.

### Load the Package

```{r library, eval=FALSE}
library(pubmedr)
```

### Define a Search Instance

You need to define a search instance that contains the query parameters for fetching data from PubMed.

```{r search,  eval=FALSE}
search <- list(
  query = "(Alzheimer OR dementia OR cognitive impairment) AND (urine) AND (early detection OR disease monitoring OR diagnosis)",
  since = as.Date("2020-01-01"),
  until = as.Date("2021-01-01"),
  publication_types = c("journal"),
  reached_its_limit = function(label) { FALSE },
  add_paper = function(paper) { print(paper) }
)
```

### Run the Search

Use the `run` function to fetch papers from PubMed based on the defined search parameters.

```{r run_search, eval=FALSE}
run(search)
```

